Regression modellining

### 2014-02-11 article2013.Rmd
Pientä päivtystä. Huomenna iso remmi päälle

---
title: "Attributions for Poverty in Post-Socialist Countries"
author: [Markus Kainu & Mikko Niemelä]
date: February 11, 2014
abstract: Utilising The Life in Transition Survey (LiTS) conducted in 2010, the purpose of the paper is to examine public perceptions of the causes of poverty in Europe and Western Asia with special emphasis on post-socialist countries. The study applies multilevel techniques in order to analyse the role of individual and country-level explanatory factors as determinants of poverty attributions. As country-level determinants, paper analyses the changes in country's economic performance during the period of global financial crises, income inequality and the state of democracy. As individual-level determinants, the paper tests to what extent risk factors related to financial hardship are associated with perceptions of the causes of poverty.
keywords: poverty
output:
  pdf_document:
    toc: true
    highlight: zenburn
  html_document:
    toc: true
    theme: flatly
---

@@

# Introduction

@@

# Prior findings on cross-national differences

@@

# Risks factors as an individual-level determinants of perceptions

@@

# Research design

@@

<!--
![Countries used in the analysis](figure/mapplot.pdf)
-->

@@

# Results

@@

## Descriptive statistics

@@

## Determinants of perceptions

@@

=======

@@

>>>>>>> gh-pages

@@

## Multilevel analysis

*As the main controbution of our study relates to cross-national variation of attributions for poverty within post-socialist countries, we shall largely focus on the effects of contextual variables. Nevertheless, as we are covering several countries that haven't been included in previous studies of individual level determinants, we shall also look carefully at the individual level.*

@@

<!-- As the main controbution of our study relates to cross-national variation of attributions for poverty within post-socialist countries, we shall largely focus on the effects of contextual variables. Nevertheless, as we are covering several countries that haven't been included in previous studies of individual level determinants, we shall also look carefully at the individual level. -->

@@

# Conclusions

@@

# References

>>>>

---
title: Attributions for Poverty in Post-Socialist Countries
author: [Markus Kainu & Mikko Niemelä]
date: February 11, 2014
abstract: Utilising The Life in Transition Survey (LiTS) conducted in 2010, the purpose of the paper is to examine public perceptions of the causes of poverty in Europe and Western Asia with special emphasis on post-socialist countries. The study applies multilevel techniques in order to analyse the role of individual and country-level explanatory factors as determinants of poverty attributions. As country-level determinants, paper analyses the changes in country's economic performance during the period of global financial crises, income inequality and the state of democracy. As individual-level determinants, the paper tests to what extent risk factors related to financial hardship are associated with perceptions of the causes of poverty.
keywords: poverty
output:
  pdf_document:
    toc: true
    number_section: true
    highlight: zenburn
  html_document:
    toc: true
    theme: flatly
---

@@

Introduction
==============================================

@@

Prior findings on cross-national differences
==============================================

@@

Risks factors as an individual-level determinants of perceptions
==============================================

@@

Research design
==============================================

@@

![Countries used in the analysis](figure/mapplot.pdf)

@@

Results
==============================================

@@

Descriptive statistics
----------------------------------------------

@@

Determinants of perceptions
----------------------------------------------

@@

@@

@@

Multilevel analysis
-------------------------------------------------

As the main controbution of our study relates to cross-national variation of attributions for poverty within post-socialist countries, we shall largely focus on the effects of contextual variables. Nevertheless, as we are covering several countries that haven't been included in previous studies of individual level determinants, we shall also look carefully at the individual level.

@@

@@

Conclusions
==============================================

@@

References
==============================================

### 2014-02-11 compareWaves.Rmd
Some Sunday evening edits..
Pientä päivtystä. Huomenna iso remmi päälle

# Comparing waves 2006 and 2010

```{r, eval=FALSE, echo=FALSE}
library(knitr)
library(markdown)
knit2html('compareWaves.Rmd', 
          stylesheet="~/workspace/web/css/rmarkdown.css",
          options = c('toc', markdown::markdownHTMLOptions(TRUE)))
```

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=TRUE,eval=TRUE, cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=10)
```

>>>>

---
title: Comparing waves 2006 and 2010 
output:
  html_document:
    toc: true
    theme: flatly
---

### 2014-02-11 mapPlots.Rmd
Pientä päivtystä. Huomenna iso remmi päälle

# Spatial visualization

@@

```{rmapPlotsDV5}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = not.stated)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

@@

```{rmapPlotsDV6}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = dont.know)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

@@

```{rmapPlotsIvMacro1}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = gdpchange07.10)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low=muted("red"), high=muted("blue")) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

### Gini coefficient

```{rmapPlotsIvMacro2}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = uw_gini)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low=muted("blue"), high=muted("red"), midpoint=33.55) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

>>>>

---
title: Spatial visualization
output:
  html_document:
    toc: true
    theme: flatly
---

@@

```{rmapPlotsDV5}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = notStated)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

@@

```{rmapPlotsDV6}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = dontKnow)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

@@

```{rmapPlotsIvMacro1}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = gdpChange)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low=muted("red"), high=muted("blue")) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

### Perceived Gini coefficient

```{rmapPlotsIvMacro2}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = perGini)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low=muted("blue"), high=muted("red"), midpoint=33.55) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

### 2014-02-11 regressionModelling.Rmd
Getting back to business. Nothing changed, but rerunning the script.
Pientä päivtystä. Huomenna iso remmi päälle

# Regression modellining

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=FALSE,eval=FALSE, cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=10)
```

@@

```{rmultilevelBivarIndOuputNOCI, results='asis'}
library(texreg)
htmlreg(list(biind.1,biind.2,
          biind.3,biind.4,
          biind.5,biind.6,
          biind.8,
          biind.9,biind.10,
          biind.11,biind.12,
             biind.13),
        #custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        use.packages=FALSE,
        include.pvalues=TRUE,
        caption="Bivariate individual blame", 
        caption.above=TRUE)

@@

>>>>

---
title: Regression modellining
output:
  html_document:
    toc: true
    theme: flatly
---

@@

```{rmultilevelBivarIndOuputNOCI, results='asis'}
library(texreg)
htmlreg(list(biind.1,biind.2,
          biind.3,biind.4,
          biind.5,biind.6,
          biind.8,
          biind.9,biind.10,
          biind.11,biind.12,
             biind.13),
        #custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        use.packages=FALSE,
        include.pvalues=TRUE,
        caption="Bivariate individual blame", 
        caption.above=TRUE)
```

@@

# Tables for presentation

## Partial
